{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-04 Paper/main.tex
Grammarly First Run

	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, but only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf. \cite{levitin_introduction_2007}).
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).

	 In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions which could be the absorption of the Near-infrared (NIR) spectrum which will be used for the simulation and application. NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of its waves on a sample to analyse the interaction of each other. {\color{green} For more details refer to the appendix SECTION ??!??!}.  This dataset can then be used to perform Functional Linear Regression (FLR) on a scalar response variable. To conduct functional linear regression, several new concepts and methods need to be considered and explained that distinguish it multivariate linear regression.
%	 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI) to where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
The focus of this paper is to introduce FLR in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:

@@

	 where the $X_{i}$ are realizations of a random function $\mathbf{X}$, $Y_i$ are the corresponding realizations of the response variable and $\beta(s)$ is the coefficient function. The distinct feature of this framework is that the regressor is a function, which necessitates a different approach to estimation. As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(s)$ for prediction. For instance, fluctuation in $X_i(s)$ at a point $s_0$ will not have any effect on $Y_i$ if $\beta(s_0)$ = 0. \\
	 Estimation of $\beta(s)$ is inherently an infinite-dimensional problem. In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion. We report the results of the Monte-Carlo simulation regarding these three different methods in Section 3. Finally, in Section 4, we test the prediction of FLR in a real-world setting. {\color{red} (We may put some simple descriptions of results about each of MC and Application)}

	\section{Theory}
	In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$. However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite dimensional space. To understand functional linear regression and the differences between the methods presented in this paper, it is therefore necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects. One integral concept in inferential statistics are random variables. Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.\\
	A typical case known to every undergraduate student of economics is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers. As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space. A formalization of this idea makes some more theoretical considerations necessary. The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015}.

@@

	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
	The inner product naturally defines a norm and an associated distance on the vector space as follows.

@@

	The closed span $\overline{span}(S)$ of a sequence $S$ in $\mathbb{H}$ is defined as the closure of the span with respect to the distance induced by the norm. $S$ is called a basis of $\mathbb{H}$ if $\overline{span}(S) = \mathbb{H}$. \\
	It is called an orthonormal basis, if in addition the following properties hold.

@@

	As can be seen, differing from the case of a Banach space, these representations can be limits of series as previously hinted at by using the closed span of the basis. As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements of a Hilbert space, is to use a truncated series.

@@

	%All functions $f$ satisfying the above condition are called square-integrable functions. 
	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. Its inner product is defined as

@@

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis but analogous constructions can be made for every closed interval of $\mathbb{R}$. 
	%Therefore, we focus on the interval $[0,1]$ without loss of generality for the purpose of this paper. 
	A random function defined on $\mathbb{L}^2[0,1]$ is a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$. The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.
	%Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations. For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.

@@

	\subsection{Functional Data Set}
	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$:

@@

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points. As it can be seen, the measurmant points can be differentiated through each sample. However, this is not a primary interest of this paper, and, therefore, we consider the case where every measurement point exists evenly, namely, that $t_{i,j}$ and $J_i$ are identical for all $i$. In principal, the recorded functional data can be seen as a set of discretized realizations of a random function since it is finitely countable. It causes necessities to represent the functional data with respect to some expansion technique. The several techniques to make the functional data smooth is introduced on the following sub-chapters.\\
	As in the finite dimensional setting, the concept of identically distributed and independent data is important for the functional data analysis. The random functions share the identical and independent distribution, which makes the statistical inferential procedures possible. An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples in which each spectra was randomly selected and evenly measured.

@@

	Both of these can be used to express or in the case of the b-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions. Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $X(\omega_0) = x(t)$ of $X(\omega)$.

@@

	\paragraph{Monomial Basis}
	{\color{red} No shift parameter in implementation in fda.}  Monomial bases are trivially decompositions of every polynomial function. The class of non-polynomial but enough many differentiable functions can be apporximated by Taylor series, a special type of power series. From these concepts, a function can be smooth by a power series. The bases construct

@@

	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^i, \quad i \in \mathcal{I}
	\end{equation}
	where the shift parameter $\alpha$ is specified to be the center of the interval subject to approximation. The first order function within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). There exist collinearity problems of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation. This restricts the number of basis functions. However, the lower order monomial function makes it impracticable to capture pronounced local peculiarities. It finally leads to an undesirable behavior at the tails such as Taylor expansion (cf. \cite{ramsay_functional_2005}). Therefore, regarding the use, this may be useful for relatively simple functions.

	\paragraph{Fourier Basis}
	Fourier series basically decomposes a periodic function with a weighted summation of trigonometric functions. Imagine that an arbitrary function in $\mathbb{L}^2[0,1]$ has one or more cycles between 0 and 1, and we can then apply the Fourier series to approximate the function for smoothing. As the series originated from the amplitude-phase form regarding cosine functions, it can be rewritten by sine and cosine form through a simple trigonometry formula, which restricts the use of an odd number of Fourier basis functions. That is why the Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
	\begin{equation}
		\phi_{i}^{F}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}

	Therefore, its basis functions inherits a repeating behavior which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots. On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree. Additionally, at each $\tau_l$ the the polynomials on neighbouring subintervals must match derivatives up to order $m-2$.
	A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}. Let $\phi_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.

@@

	This, however, does not really yield a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$. To really obtain a basis of $\mathbb{L}^2[0,1]$ from B-splines, further theoretical considerations about, for example, infinite series of B-splines and specific knot choices would have to be made. As this is out of the scope of this paper, for the sake of simplicity, we will assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen B-spline basis. 
	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.

@@

	\subsection{Approximation and Smoothing via Basis Truncation}
	As above-mentioned, the realized curves can be estimated with basis functions. For the basis expansion, it is technically possible to use all basis functions $\phi_{j \in \mathcal{I}}$ to fit an completely unbiased estimate. This is not efficient since the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis. On the other hand, the important information on the curves could be missed with a too-small number of basis functions. In that sense, this discussion is subject to the Bias-Variance Tradeoff. It challenges the researcher to seek a point at which they truncate the basis function to remove noise and, at the same time, not to introduce too much bias by maintaining significant fluctuations of the curves. The basis expansion with truncation is defined by
	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}
	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$. The number $L$ can be chosen subjectively, but also through applying a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or other criteria. The significance of this choice of truncation becomes more evident in {\color{green} Link estimation} and is the subject of the simulation study.

	\subsection{Functional Data Sets}
	{\color{orange} Move this part below 3.2?}
	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$:

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points. As it can be seen, the measurmant points can be differentiated through each sample. However, this is not a primary interest of this paper, and, therefore, we consider the case where every measurement point exists evenly, namely, that $t_{i,j}$ and $J_i$ are identical for all $i$. In principal, the recorded functional data can be seen as a set of discretized realizations of a random function since it is finitely countable. The several basis systems to make the functional data smooth is introduced from the next sub-chapter.\\
	As in the finite dimensional setting, the concept of identically distributed and independent data is important for the functional data analysis. The random functions share the identical and independent distribution, which makes the statistical inferential procedures possible. An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples in which each spectra was randomly selected and evenly measured.

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process. To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2[0,1]$. Therefore, let $X: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function. Then the mean and covariance functions of $X$ are defined as follows.
	%To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix. Let therefore $V(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(V(\omega)) = \mu_V$ and $Cov(V(\omega)) = \Sigma_V$. Then $\Sigma_V$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_V = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\

	%This decomposition can be used to express the random vector $V(\omega)$ in the following way.

	%\begin{equation}
	%	V(\omega) = \mu_V + \Gamma \Lambda^{\frac{1}{2}} D(\omega) = \mu_V + \sum_{i = 1}^{p} \sqrt{\lambda_i} D_i(\omega) \gamma_i
	%\end{equation}

	%where $D(\omega)$ is a random vector with $\mathbb{E}(D(\omega)) = 0_p$ and $Cov(D(\omega)) = \mathbb{I}_p$.\\

@@

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}
	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
	\begin{equation}\label{HSKernal}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
	\end{equation}

@@

	%The $\xi_j(\omega)$ are then given as 
	%\begin{equation}
	%	\xi^m(\omega) = \langle X(\omega) - \mu, \nu^m\rangle = \int_{0}^{1} \left(X(\omega)(s) - %\mu(s)\right) \nu^m(s) \mathrm{d}s
	%\end{equation} 
	%and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.
	\begin{multicols}{2}
		\begin{enumerate}
			\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
			\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = \delta^{m,n}\lambda^m$%0$ if $m \neq n$
			\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
		\end{enumerate}
	\end{multicols}
	where $\delta^{m,n} = 0$ if $m \neq n$, otherwise 1.
	In the typical scalar setting, a similar consideration leads to the concept of principal components. This is also possible in a functional setting. Let $\{x_1(t), \dots, x_n(t)\}$ be a set of i.i.d. realizations generated by a random function $X(\omega) \mapsto \mathbb{L}^2[0,1]$.
	Define the following sample analogues for the mean and covariance functions.

@@

	In reality these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation. For the sake of clarity the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.

@@

	\subsection{Scalar-on-Function Regression}
	In the simple scalar setting one of the most important tools in econometrics is the linear regression. Its goal is to predict the value of a dependent variable given a set of associated variables. For reference assume a data generating process as follows. {\color{red} Structure is bad... This will be changed.}

@@

	Where $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
	In this finite dimensional setting one important question is how to estimate the unknown coefficients $\beta$. The most well known estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions. {\color{red}List Assumptions? Then we need to list the assumptions for functional linear regression as well I think.}

@@

	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is supposed to be predicted from a functional variable. 
	A general data generating process in this functional scenario could look like the following equation.

	\begin{equation}
		Y(\omega) = \alpha + \Psi\left(X(\omega)\right) + \epsilon(\omega)
	\end{equation}

	Here $\Psi$ is a functional that maps a realization of a random function in $\mathbb{L}^2[0,1]$ into $\mathbb{R}$. One simple example to illustrate the principle is the maximum $\Psi(f) = \max_{x \in [0,1]}f(x)$.
	However, the typical setup is often as follows mimicking the structure of the multivariate linear model extended from summation to integration. This structure is crucial for the extension of linear regression to the case of functional regressors. Therefore, in this paper we always implicitly assume that a data generating process has the following structure. {\color{red} maybe a better motivation is the one Jona gave: from very dense observations that run into problems of colinearity when using the original OLS estimator}

@@

	Where $x(t)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(t)$ is an unknown coefficient function. 
	Similar to the finite dimensional setting, an interesting question is how to estimate the unknown function $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables. However, a simple extension of the OLS estimator to allow for infinite dimensional objects is not possible. Therefore, other options have to be considered.

@@

	As these theoretical Eigenfunctions and Eigenvalues are typically unknown, the corresponding equation in sample analogues is more interesting as a representation of an observation.

@@

	%\subsection{Draft-Overview}
	%\begin{itemize}
	%	\item Motivate Simulation for some data generating process from application
	%	\item Describe Simulation Setting from technical standpoint (DGP, set-up for replication, ...)
	%			\item Prediction not Inference (Alternative: Focused on a testing procedure motivated by the application)
	%	\item Present Results
	%	\item Explain relevance for application
	%\end{itemize}

>>>>

	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf. \cite{levitin_introduction_2007}).
	As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).

	In functional data analysis, the concept of a data set can include not only realizations of scalar random variables but also realizations of random functions. These could be the absorption of the Near-infrared (NIR) spectrum, which will be used for the simulation and application. NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of its waves on a sample to analyze the interaction of each other. {\color{green} For more details refer to the appendix SECTION ??!??!}.  This dataset can then be used to perform Functional Linear Regression (FLR) on a scalar response variable. To conduct functional linear regression, we need to consider several new concepts and methods that distinguish it from multivariate linear regression.
%	 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI) to where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as follows:

@@

	 where the $x_{i}$ are realizations of a random function $X(\omega)$, $y_i$ are the corresponding realizations of the response variable and $\beta(s)$ is the coefficient function. The distinct feature of this framework is that the regressor is a function, which necessitates a different approach to estimation. As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(t)$ for prediction or inference. 
	 %For instance, fluctuation in $x_i(s)$ at a point $s_0$ will not have any effect on $Y_i$ if $\beta(s_0)$ = 0. \\
	 The estimation of $\beta(s)$ is inherently an infinite-dimensional problem. In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion. We report the results of the Monte-Carlo simulation regarding these three different methods in Section 3. Finally, in Section 4, we test the prediction of FLR in a real-world setting.

	\section{Theory}
	In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$. However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space. Therefore, it is necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects. One integral concept in inferential statistics is random variables. Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.\\
	A typical case known to every undergraduate student of economics is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers. As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space. A formalization of this idea makes some more theoretical considerations necessary. The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015}.

@@

	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
	The inner product naturally defines a norm and an associated distance on the vector space.

@@

	The closed span $\overline{span}(S)$ of a sequence $S$ in $\mathbb{H}$ is defined as the closure of the span with respect to the distance induced by the norm. $S$ is called a basis of $\mathbb{H}$ if $\overline{span}(S) = \mathbb{H}$. \\
	It is called an orthonormal basis if, in addition, the following properties hold.

@@

	As can be seen, differing from the case of Banach spaces, these representations can be limits of series as previously hinted at by using the closed span of the basis. As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements of a Hilbert space is to use a truncated series.

@@

	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. Its inner product is defined.

@@

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis, but analogous constructions can be made for every closed interval of $\mathbb{R}$. 
	%Therefore, we focus on the interval $[0,1]$ without loss of generality for the purpose of this paper. 
	A random function defined on $\mathbb{L}^2[0,1]$ is a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$. The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.

@@

	\subsection{Functional Data Sets}
	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$:

@@

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points. The measurement points can be different for each sample. However, this is not a primary interest of this paper, and, therefore, we consider the case where curves are observed at a shared set of measuring points. In principle, these measurements can be seen as a discretized approximation of a realization of a random function. It causes necessities to represent the functional data with respect to some expansion technique. One technique to make the functional data smooth, truncated basis expansion, is introduced in the following sections.\\
	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis, such as, for example, many inferential procedures. One example could be a set of NIR absorption spectra of gasoline samples in which curves are observed at a shared set of wavelengths and each sample stemming from the same production can be seen as a realization of the same random process.

@@

	Both of these can be used to express or in the case of the B-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions. Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $X(\omega_0) = x(t)$ of $X(\omega)$.

@@

	{\color{red}We should give a reference for how to obtain these coefficients and say that for the purpose of this paper we will treat this as a black box.}

	\paragraph{Monomial Basis}
	{\color{red} No shift parameter in implementation in fda.} The Monomial basis are trivially decompositions of every polynomial function. The class of non-polynomial but enough many differentiable functions can be approximated by Taylor series, a special type of power series. From these concepts, a function can be smooth by a power series. The bases construct

@@

	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^i, \quad i \in \mathcal{I}
	\end{equation}
	where the shift parameter $\alpha$ is specified to be the center of the interval subject to approximation. The first order function within the monomial basis system, for $k=0$, is called the constant basis (cf. \cite{horvath_inference_2012}). There exist collinearity problems of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation. This restricts the number of basis functions. However, the lower order monomial function makes it impracticable to capture pronounced local peculiarities. It finally leads to an undesirable behavior at the tails such as Taylor expansion (cf. \cite{ramsay_functional_2005}). Therefore, regarding the use, this may be useful for relatively simple functions.

	\paragraph{Fourier Basis}
	Fourier series decomposes a periodic function with a weighted sum of trigonometric functions. Imagine that an arbitrary function in $\mathbb{L}^2[0,1]$ has one or more cycles between $0$ and $1$, and we can then apply the Fourier series to approximate the function for smoothing. As the series originated from the amplitude-phase form regarding cosine functions, it can be rewritten by sine and cosine form through a simple trigonometry formula, which restricts the use of an odd number of Fourier basis functions. That is why the Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
	\begin{equation}
		\phi_{i}^{F}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}
	Therefore, its elements inherit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots. On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree. Additionally, at each $\tau_l$ the polynomials on neighboring subintervals must match derivatives up to order $m-2$.
	A B-spline is a specific type of spline belonging to a basis system developed by \cite{de_boor_practical_1978}. Let $\phi_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.

@@

	However, a finite set of B-spline functions does not constitute a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$. To really obtain a basis of $\mathbb{L}^2[0,1]$ from B-splines, further theoretical considerations about, for example, infinite series of B-splines and specific knot choices would have to be made. As this is out of the scope of this paper, for the sake of simplicity, we will assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen B-spline basis. 
	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.

@@

	\subsection{Approximation and Smoothing via Basis Truncation}
	As mentioned above, the realized curves can be expressed in terms of a chosen functional basis. For this expansion, it is technically possible to use a complete basis of $\mathbb{L}^2[0,1]$. In many cases this is not a desirable approach as the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis. {\color{red} Therefore, methods such as acceleration penalties have to be employed to smooth the function.} On the other hand, important information on the curves could be missed by using a number of basis functions that is too small. In that sense, this discussion is subject to the Bias-Variance tradeoff. It challenges the researcher to seek a point at which they truncate the basis function to remove noise and, at the same time, not to introduce too much bias by maintaining significant fluctuations of the curves. The basis expansion with truncation is defined by
	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}
	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$. The number $L$ can be chosen subjectively, but also through applying a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or other criteria. The significance of this choice of truncation becomes more evident in {\color{green} Link estimation} and is the subject of the simulation study.

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
	Given a realization of a random function $X: \Omega \mapsto \mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process. To do so, it is necessary to define the mean and covariance functions of $X(\omega)$.

@@

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}

	where the $c(t,s)$ are Hilbert-Schmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by

	\begin{equation}\label{HSKernal}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
	\end{equation}

@@

	%The $\xi_j(\omega)$ are then given as 
	%\begin{equation}
	%	\xi^m(\omega) = \langle X(\omega) - \mu, \nu^m\rangle = \int_{0}^{1} \left(X(\omega)(s) - %\mu(s)\right) \nu^m(s) \mathrm{d}s
	%\end{equation} 
	%and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.
	\begin{multicols}{2}
		\begin{enumerate}
			\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
			\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = 0$ if $m \neq n$
			\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
		\end{enumerate}
	\end{multicols}

	In the scalar setting, a similar consideration leads to the concept of principal components, which can be extended to the functional setting. Let $\{x_1(t), \dots, x_n(t)\}$ be a set of i.i.d. realizations generated by a random function $X(\omega) \mapsto \mathbb{L}^2[0,1]$.
	Define the following sample analogs for the mean and covariance functions.

@@

	In reality, these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation. For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.

@@

	\subsection{Scalar-on-Function Regression}
	In the simple scalar setting, one of the most important tools in econometrics is linear regression. Its goal is to predict the value of a dependent variable given a set of associated variables. For reference, assume a data generating process as follows.

@@

	Where $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
	In this finite dimensional setting one important question is how to estimate the unknown coefficients $\beta$. The most well known estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions.

@@

	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is supposed to be predicted from a functional variable. 
	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects. Therefore, we will always assume a data generating process as follows in this paper.

@@

	Where $\beta(t)$ is an unknown coefficient function. Similar to the finite-dimensional setting, an interesting question is how to estimate $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables. However, a simple extension of the OLS estimator to allow for infinite-dimensional objects is not possible. Therefore, other options have to be considered.

@@

	As these theoretical Eigenfunctions and Eigenvalues are typically unknown, the corresponding equation in sample analogs is more interesting as a representation of an observation.

@@
